Modeling and leveraging intuitive theories to improve vaccine attitudes

### 2022-02-15 paper/paper-papaja.Rmd
references fixed

note: |
  This manuscript has not yet been peer-reviewed.

@@

keywords          : "Intuitive theories; Belief revision; Vaccine attitudes; Cognitive modeling"
wordcount         : "9163"

>>>>

note: |
  This manuscript has not yet been peer-reviewed (2/15/2022).

@@

keywords          : "Intuitive theories; Belief revision; Vaccine attitudes; Cognitive modeling"
wordcount         : "9161"
